# Bookdown Guide {#bookdown}

The first step to edit and add to this bookdown is to install the **bookdown** package from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

## Primary Reference Resources

Here is a list of resources to learn how to use and edit in bookdown

- [Bookdown Package Documentation](https://bookdown.org/)
- [Authoring Books with R Markdown](https://bookdown.org/yihui/bookdown/)
- [R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/)
- [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)

## Formatting

You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

Remember each Rmd file contains one and only one chapter, and **a chapter** is defined by the first-level heading `#`.

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

## Citations

You can easily write citations using .bib files within this repository formatted using [BibTEX](http://www.bibtex.org/). For example, the **bookdown** package [@R-bookdown] in this reference book, which was built on top of R Markdown and **knitr** [@xie2015].

## Alt Text for Accessibility

[Use the knitr package to add alt text to graphics in R Markdown files](https://www.rstudio.com/blog/knitr-fig-alt/)

## Rendering Bookdown to Build & Publish

In your Console, type either of these commands depending on which type of render you prefer:

`bookdown::render_book("index.Rmd", "bookdown::gitbook")`
`bookdown::render_book("index.Rmd", "bookdown::pdf_book")`

To compile to PDF, you need XeLaTeX. It is recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.
